### 2023-01-24 manuscript.tex
STIX2 fonts [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/1c02a3ca58bd5ba01fcd0dd7266edfe5376fb0c4.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/1c02a3ca58bd5ba01fcd0dd7266edfe5376fb0c4/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4001413120

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/fa45efa5c79f23abe61e9b521cf4269293651d36/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/fa45efa5c79f23abe61e9b521cf4269293651d36}{stain/2022-fdo-paper@fa45efa}
on January 24, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/1c02a3ca58bd5ba01fcd0dd7266edfe5376fb0c4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/1c02a3ca58bd5ba01fcd0dd7266edfe5376fb0c4}{stain/2022-fdo-paper@1c02a3c}
on January 24, 2023.
